---
title: "Bonferroni Function Development"
author: "Mike Seaman"
date: "2 April 2020"
output: html_notebook
---

This notebook is for developing a function that will construct Bonferroni
confidence intervals.

This is the bonf_ci function. 

```{r}

bonf_ci <- function(the_data, the_pairs, conf_level) {
  
# These next two lines are to create vectors for both the lower and upper
# bounds of the confidence interval.
  
  lb <- 1:nrow(the_pairs)
  ub <- 1:nrow(the_pairs)
  
# Now I add these to the matrix that we will return, but first I copy the
# designation of pairs.
  
  the_cis <- cbind(the_pairs, lb, ub)
  
# I now calculate the confidence level when we have a number of comparisons.
# Now that I can determine the number of comparisons with the numbe of rows
# in the pairs matrix.
  
  pair_conf = 1- (1 - conf_level)/nrow(the_pairs)
  
# Now I loop for the number of comparisons that I am using to construct
# confidence intervals.
  
  for (i in 1:nrow(the_pairs)){
    
# This pulls out the data that I need for the comparison on the designated
# row, which is tracked by "i" in the loop.

    pair <- subset(the_data, the_data[, 1] == the_pairs[i, 1] |
                    the_data[, 1] == the_pairs[i, 2])
    
# This calculates the confidence interval.    
    
    t_results <- t.test(pair[, 2] ~ pair[, 1], conf.level = pair_conf)
    
# These lines pull out the lower and upper bounds and add them to the matrix
# that I'm going to return.
    
    the_cis[i,3] <- t_results$conf.int[1]
    the_cis[i,4] <- t_results$conf.int[2]
  }
  
  return(the_cis)
}

```


This is for testing the bonf_ci function with the hsb2 data. I assume that the
hsb2 data are in the same directory as this notebook.

```{r}

hsb2 <- read.csv("hsb2.csv")


# This is going to create the matrix to send to the function with my data.

my_data <- cbind(hsb2$ses, hsb2$math)

# This is going to select two pairs for testing and put them in a matrix.

first <- c(3, 2)
second <- c(1, 1)
my_pairs <- cbind(first, second)

# And now the grand test!

bonf_ci(my_data, my_pairs, .95)

```

#### Future enhancements

Here are some ideas for the future.

* Make it clear which way the means are subtracted

* Be able to send a data frame instead of a matrix

* Be able to send all the data and then indicate which variables to use in the
comparisons

* Be able to use a factor instead of numbers for the explanatory variable

* Include some error checking, such as making sure the user picked groups 
that are actually in the data

* Be able to do complex comparisons, not just pairwise
